\chapter{Summary and Implication}
\label{chap:summary}

\section{Exotic hadrons study at \lhcb}

The first observation of exotic states with a new quark content $\ccbar u\squarkbar$ decaying to the $\jpsi K^+$ final state is reported 
with high significance from an amplitude analysis of the $\Bp \to \jpsi \phi K^+$ decay in Chapter.~\ref{chap:Zcs_study}. 
The analysis is carried out using proton-proton collision data corresponding to a total integrated luminosity of 9\invfb collected 
by the LHCb experiment at centre-of-mass energies of $7$, $8$ and $13$\tev. 
The most significant state, $Z_{cs}(4000)^+$, 
has a mass of $4003\pm6^{+\phantom{0}4}_{-14}\mev$, 
a width of $131\pm15\pm26\mev$, 
and spin-parity $1^+$, where the quoted uncertainties are statistical and systematic, respectively. 
A new $1^+$ $X(4685)$ state decaying to the $\jpsi \phi$ final state is also observed with high significance.
In addition, 
the four previously reported $\jpsi \phi$ states are confirmed and two more exotic states, $Z_{cs}(4220)^+$ and $X(4630)$,  
are observed with significance exceeding five standard deviations.

The $Z_{cs}(4220)^+$ observed at \lhcb is not as same as the one discovered at \besiii,
we need to examine them in future experriments carefully.
Besides,
the neutral isospin particle of $Z_{cs}(4000)^+$ and $Z_{cs}(4220)^+$ can be searched in an akin decay chennel,
$\Bz\to\jpsi\phi\KS$,
which can be studied at \lhcb.


The first observtion of $\Lb\to\Lc\Kp\Km\pim$ decay is reported in Chapter.~\ref{chap:open_pentaquark},
and the ratio branching fraction to $\Lb\to\Lc\Dsm$ decay is measured to be $(9.26 \pm 0.29 \pm 0.46 \pm 0.26)\times10^{-2}$. 
Though no obvious open charm pentaquark signal is observed from the $\Lc\Kp$ mass distribution,
some analogous decay channels can be explored to search this kind of states at \lhcb.
It is very likely that the open-charm pentaquark states can be found in futher studies
as the open-charm tetraquark state was observed at \lhcb recently\supercite{LHCb-PAPER-2020-015}. 
%as the open-charm tetraquark state was observed at \lhcb recently. 

In addition,
there are many other open questions related pentaquark sector.
The $J^{P}$ of observed pentaquarks have not been determined yet,
we expect these important parameters can be explored at \lhcb. 
%The $J^{P}$ of observed pentaquarks are expected to be determined from an updated amplitude analysis with Run 1 and Run 2 by \lhcb.
Considering the pentaquark states are only found in $\Lb\to\jpsi\proton\Km$ at \lhcb,
it is necessary to confirm these observations in different decay channels or different experiments.
%Confirm the pentaquark states in cabbibo-supressed decay $\Lb\to\jpsi\proton\pim$ with larger data sample after Run 3.


\section{\ecal simulation for \upgradetwo at \lhcb}

This dissertation discusses the simulation study of \ecal for \lhcb \upgradetwo.
Two simulation tool were developed from this research.
According to two decay channels,
it is found that the precision timing and smaller cell size are keys for \upgradetwo of \ecal.
Besides,
the high granularity Si-W \ecal can meet these requirements.

As the final upgrade plan of \ecal for \upgradetwo at \lhcb has not been decided yet,
it is important to continue detailed simulation study for \ecal \upgradetwo.
For example,
the final cell size segmenation should be optimized based on some key decay channels,
the precision timing is used to identify different kinds of shower,
the detailed reconstruction algorithms need to be optimized and so on.
When the final scheme is chosen,
the detailed detector model can be imported in \lhcb software framework. 




